A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
fix
misc edits

In Table~\ref{tab:graphalytics} we show the results from running Graphalytics on the Dota-League dataset. An explanation of each algorithm is given in \cite{Iosup:2016:Graphalyticstech}. Table~\ref{tab:graphalytics} shows only a broad overview of the two systems: GraphBIG and PowerGraph. In general, we see GraphBIG is more performant. However, results such as these are preliminary and do not show the complete picture.

@@

\todo{rework this. It would be nice to compare Graphalytics and our approach on the real-world dataset.}
Table~\ref{tab:epg-perf}, in contrast, gives an overview of the performance results of running graphalytics and our approach using the same dataset [TODO: Get the Dota-League Dataset working with easy-parallel-graph and replace Table~\ref{epg-perf}]. Table~\ref{tab:epg-perf} shows the average time across 32 roots, whereas Graphalytics by default shows results for a single root.

Figures~\ref{fig:bfs-time} and \ref{fig:sssp-time} show performance results for a Kronecker graph with scale $22$. The box plots give an idea of the runtime distributions. There is less discrepancy between the runtimes of SSSP (between 0.1 and 1.7 seconds) compared to BFS (0.01 and 1.7 seconds) but GAP is the clear winner in both cases. The data structure construction times for GAP and GraphMat are consistent; in both cases the platforms create the same data structure for both algorithms. These results are consistent with \cite{Sundaram:2015:GraphMat} which lists GraphMat as more performant than PowerGraph in SSSP.

@@

\begin{figure}
	\centering
	\begin{minipage}{0.59\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/sssp_time.pdf}
	\end{minipage}
	\begin{minipage}{0.365\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/sssp_dsc.pdf}
	\end{minipage}
	\caption{The $y$-axes is logarithmic. The left box plot shows the time to compute the SSSP starting at the same 32 roots as Fig.~\ref{fig:bfs-time}. Both PowerGraph and GraphBIG construct their data structures at the same time as they read in the file.}
	\label{fig:sssp-time}
\end{figure}

@@

We attempt to use similar stopping criteria for each system, but GraphMat executes until no vertices change rank; effectively its stopping criterion requires the $\infty$-norm be less than machine epsilon. This could account for the increased number of iterations. We adjusted the other systems to use $\sum_{k=1}^{n} |p_k^{(i)} - p_k^{(i-1)}| < \epsilon $ as the stopping criteria, where $i$ is the iteration and $n$ is the number of vertices. We use $\epsilon = 6 \times 10^{-8}$ because this value is approximately machine epsilon for a single precision floating point number. This is done with the goal of making the stopping criteria as similar as possible.

@@

\begin{table}
	\caption{The data are generated using a Kronecker graph with a scale of 22. Sleeping Energy refers to the power (in Watts) consumed during the \texttt{unistd} C \texttt{sleep} function, multiplied by the Time row. Essentially, this measures the amount of energy that would have been consumed even if nothing was running. The increase over sleep is the ratio of the first and third columns. These are all averaged over 32 roots.}
	\centering
	\begin{tabular}{l|r|r|r|r}
			&	GAP  &    Graph500 & GraphBIG & GraphMat \\ \hline
		Time (s) &  0.01636 & 0.01884 & 1.600 & 1.424 \\
		Average Power per Root (W) & 72.38 & 97.17 & 78.01 & 70.12 \\
		Energy per Root (J) &	1.184 & 1.830 & 112.213 & 111.104 \\
		Sleeping Energy (J) & 0.4046  & 0.4660 & 39.591 &  35.234 \\
		Increase over Sleep & 2.926 & 3.928 & 2.834 & 3.153
	\end{tabular}
	\label{tab:power}
\end{table}

RAPL also allows the measurement of DRAM power, the results of which are shown in Fig.~\ref{fig:power}. The left plot describes the second row of Table~\ref{tab:power} in more detail. We notice a smaller spread of RAM power consumption, but still a noticeable difference. GraphMat results in the lowest RAM and power consumption despite not having the largest runtime.

>>>>

In Table~\ref{tab:graphalytics} we show the results from running Graphalytics on the Dota-League dataset. An explanation of each algorithm is given in \cite{Iosup:2016:Graphalyticstech}. Table~\ref{tab:graphalytics} shows only a broad overview of the two systems: GraphBIG and PowerGraph. In general, we see GraphBIG performs better. However, these preliminary results do not show the complete picture. 
\todo[inline]{Would be good to add something here on what more is needed for getting a complete picture.}

@@

\todo{rework this. It would be nice to compare Graphalytics and our approach on the real-world dataset.}
Table~\ref{tab:epg-perf}, by contrast, gives an overview of the performance results of running Graphalytics and our approach using the same dataset [TODO: Get the Dota-League Dataset working with easy-parallel-graph and replace Table~\ref{epg-perf}]. Table~\ref{tab:epg-perf} shows the average time across 32 roots, whereas Graphalytics by default shows results for a single root.

Figures~\ref{fig:bfs-time} and \ref{fig:sssp-time} show performance results for a Kronecker graph with scale $22$. The box plots give an idea of the runtime distributions. There is less variance in the runtimes of SSSP (between 0.1 and 1.7 seconds) compared to BFS (0.01 and 1.7 seconds) but GAP is the clear winner in both cases. The data structure construction times for GAP and GraphMat are consistent; in both cases the platforms create the same data structure for both algorithms. These results are consistent with \cite{Sundaram:2015:GraphMat} which lists GraphMat as more performant than PowerGraph in SSSP.

@@

\begin{figure}
	\centering
	\begin{minipage}{0.59\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/sssp_time.pdf}
	\end{minipage}
	\begin{minipage}{0.365\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/sssp_dsc.pdf}
	\end{minipage}
	\caption{The $y$-axes is logarithmic. The left box plot shows the time to compute the SSSP starting at the same 32 roots as Fig.~\ref{fig:bfs-time}. Both PowerGraph and GraphBIG construct their data structures at the same time as they read the file.}
	\label{fig:sssp-time}
\end{figure}

@@

We attempt to use similar stopping criteria for each system, but GraphMat executes until no vertices change rank; effectively its stopping criterion requires the $\infty$-norm be less than machine epsilon. This could account for the increased number of iterations. We adjusted the other systems to use $\sum_{k=1}^{n} |p_k^{(i)} - p_k^{(i-1)}| < \epsilon $ as the stopping criteria, where $i$ is the iteration and $n$ is the number of vertices. We use $\epsilon = 6 \times 10^{-8}$ because this value is approximately machine epsilon for a single precision floating-point number. The goal is to make the stopping criteria for all implementations as similar as possible.

@@

\begin{table}
	\caption{The data are generated using a Kronecker graph with a scale of 22. Sleeping Energy refers to the power (in Watts) consumed during the \texttt{unistd} C \texttt{sleep} function, multiplied by the Time row. Essentially, this measures the amount of energy that would have been consumed if nothing was running. The increase over sleep is the ratio of the first and third columns. These are all averaged over 32 roots.}
	\centering
	\begin{tabular}{l|r|r|r|r}
			&	GAP  &    Graph500 & GraphBIG & GraphMat \\ \hline
		Time (s) &  0.01636 & 0.01884 & 1.600 & 1.424 \\
		Average Power per Root (W) & 72.38 & 97.17 & 78.01 & 70.12 \\
		Energy per Root (J) &	1.184 & 1.830 & 112.213 & 111.104 \\
		Sleeping Energy (J) & 0.4046  & 0.4660 & 39.591 &  35.234 \\
		Increase over Sleep & 2.926 & 3.928 & 2.834 & 3.153
	\end{tabular}
	\label{tab:power}
\end{table}

RAPL also allows the measurement of DRAM power, the results of which are shown in Fig.~\ref{fig:power}. The left plot describes the second row of Table~\ref{tab:power} in more detail. We notice a smaller spread of RAM power consumption, but still a noticeable difference. GraphMat results in the lowest RAM and power consumption despite not having the shortest runtime.
